### 2013-11-22 PositionPaper/incremental.tex
no message

Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, time the system processes it according as follows: (i) SLA global computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) optimizing and integrating results. The results of these steps generate intermediate results that are stored as knowledge in order to reduce the overhead of the query evaluation process. The whole process is monitored to determine whether a computed SLA is being honoured while a query is evaluated.

 Given a query, expressed as an SQL like expression including spatio-temporal attributes and preferences, for example, {\em List of energy providers that can provision 1000 Kwatts/h, in the next 10 seconds, that are close to my city with a cost of 0,50 euros/Kwatt?}. Assuming also that energy providers are represented by services exporting their SLA agreements and that can potentially be combined for answering the query. Thus, the whole query evaluation process is done through the following steps:

\begin{enumerate}

\item  {\bf Global SLA computation}. 
This first stage can be defined as a vertical mapping SLAs given the high level SLA described by the user (i.e. macroscopic constraints: execution time, pay / no pay, data reliability, data source). The system should be able to find relevant service compositions that respond to the query and, when combined, meet the constraints imposed by the user (High level SLA).

@@

  \item {\bf Rewrite the query.} See wether a similar Q has been already rewritten or rewrite it. Executing a query requires first a semantic analysis which will subdivide R into a set of sub-queries, in such a way that each sub-query can be processed by a DataService deployed on the cloud.   The subsueries represent the possible combination of services that can answer the initial query with given SLA.

  \item {\bf Optimize and execute subqueries.} Generate a service coordination search space that can compute each subquery and can integrate the global result. 
Each subquery is optimized with respect to user profile.

  \item Dispatch the execution of subqueries, integrate them into a result. Monitor the consumption of resources, the execution, time, behaviour ofi the services and make decisions
\end{enumerate}

%-----------------------------------------------------------------
\subsection{SLA model}
\label{sec:slaModel}
%-----------------------------------------------------------------

@@

@@

%-----------------------------------------------------------------
\subsection{Executing optimized queries}
\label{sec:queryOpt}
%-----------------------------------------------------------------

>>>>

Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, time the system processes it according as follows: (i) SLA global computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) optimizing and integrating results. The results of these steps generate intermediate results that are stored as knowledge in order to reduce the overhead of the query evaluation process. The whole process is monitored to determine whether a computed SLA is being honoured while a query is evaluated. 
The following sections describe how this query is computed according to our approach.

%-----------------------------------------------------------------
\subsection{Computing query SLA}
\label{sec:slaModel}
%-----------------------------------------------------------------

This first stage can be defined as a vertical mapping SLAs given the high level SLA described by the user (i.e. macroscopic constraints: execution time, pay / no pay, data reliability, data source). The system should be able to find relevant service compositions that respond to the query and, when combined, meet the constraints imposed by the user (High level SLA).

@@

@@

See wether a similar Q has been already rewritten or rewrite it. Executing a query requires first a semantic analysis which will subdivide R into a set of sub-queries, in such a way that each sub-query can be processed by a DataService deployed on the cloud.   The subsueries represent the possible combination of services that can answer the initial query with given SLA.

@@

%-----------------------------------------------------------------
\subsection{Executing optimized queries}
\label{sec:queryOpt}
%-----------------------------------------------------------------
Generate a service coordination search space that can compute each subquery and can integrate the global result. 
Each subquery is optimized with respect to user profile.

 Dispatch the execution of subqueries, integrate them into a result. Monitor the consumption of resources, the execution, time, behaviour ofi the services and make decisions

### 2013-11-22 PositionPaper/useCase.tex
no message

\begin{figure}
\includegraphics[width=0.6\textwidth]{figs/arch.png}
\caption{\label{fig:energyXChange} Energy exchange.}
\end{figure}

@@

>>>>

\begin{figure*}
\includegraphics[width=0.6\textwidth]{figs/arch.png}
\caption{\label{fig:energyXChange} Energy exchange.}
\end{figure*}

@@

 Given a query, expressed as an SQL like expression including spatio-temporal attributes and preferences, for example, {\em List of energy providers that can provision 1000 Kwatts/h, in the next 10 seconds, that are close to my city with a cost of 0,50 euros/Kwatt?}. Assuming also that energy providers are represented by services exporting their SLA agreements and that can potentially be combined for answering the query.
